---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fuse.prep

<!-- badges: start -->
<!-- badges: end -->

The goal of **`{fuse.prep}`** is to prepare the input data for the Framework for Understanding Structural Errors ([FUSE](https://naddor.github.io/fuse/)).



## Installation

You can install the development version of **{`fuse.prep`}** from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("lhmet-ped/fuse.prep")
```


## Dados

This is a basic example which shows you how to create the elevation bands NetCDF file.

Os dados de exemplo necessários são disponibilizados com os pacotes **`{HEgis}`** (`poly74` e `condem74`) e **`{fuse.prep}`** (`precclim74`):

- polígono da bacia hidrográfica do posto do ONS (Simple Feature, `sf`)

- os dados de elevação do terreno (`raster`) hidrologicamente condicionados

- precipitação climatológica anual (`raster`)


```{r data}
library(fuse.prep)
library(HEgis)
poly74
condem74
precclim74
```

# Bandas de elevação 

https://github.com/naddor/tofu/blob/master/input_output_settings/create_elev_bands_nc.R

```{r}
elev_tab_format <- elev_bands(con_dem = condem74, meteo_raster = precclim74, dz = 100)
elev_tab_format
```

